%-------------------------
% Resume in Latex
% Author : Jad Alriyabi
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Jad Alriyabi} \\ \vspace{1pt}
    Vancouver, BC $|$ \small 778-325-1945 $|$ \href{mailto:jad.alriyabi@gmail.com}{\underline{jad.alriyabi@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/jadalriyabi/}{\underline{linkedin.com/in/jadalriyabi}} $|$
    \href{https://github.com/Jadalriyabi}{\underline{github.com/Jadalriyabi}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Simon Fraser University}{Vancouver, BC}
      {Bachelor of Science in Computer Science, Concentration in AI, Minor in Business}{Jan. 2020 -- Oct. 2024}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant Courses:} Cloud Computing, Artificial Intelligence, Data Structures and Algorithms, Cyber Security}
        \resumeItem{\textbf{Certifications:} AWS Certified Solutions Architect, Docker Certified Associate, Certified Scrum Master}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------


\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Developer - Intern}{August 2024 -- Present}
      {Absolute Security}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{Reduced bug investigation time by 30\% by designing and deploying scalable RESTful APIs integrated with cloud-based services using AWS and React JS leading to a successful tool for QA.}
        \resumeItem{Improved QA efficiency by 25\% by developing an internal LLM tool using TypeScript, PyTorch, and React.}
        \resumeItem{Reduced deployment time by 14\% by designing and deploying CI/CD pipelines for API integrations, reducing deployment time by 40\%.}
        \resumeItem{Found 8+ customer-facing defects by creating automated stress and performance tests using Pytest.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {AI Software Engineering Resident }{June 2024 -- Present}
      {Headstarter AI}{Remote}
      \resumeItemListStart
        \resumeItem{Built and deployed 5 AI projects leveraging React JS, NoSQL, and AWS, following agile methodologies with weekly sprints and incorporated CI/CD practices for iterative deployment.}
        \resumeItem{Containerized 5+ AI tools with Docker, enabling seamless deployment across cloud platforms with each built app.}
        \resumeItem{Led team of 3 engineers as principal engineer to develop an customer support agent using Next.js, integrated a custom RAG pipeline using OpenAI that responds based on a company's knowledge base.}
        \resumeItem{Scaled each web-app to 200+ users by iterating on user feedback to make continuous optimizations.}
    \resumeItemListEnd


    \resumeSubheading
      {Technical Program Manager - Coop  }{January 2024 -- August 2024}
      {Absolute Security}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{Served as Scrum Master for 3+ teams by leading scrum sessions, facilitating sprint planning sessions aligning with team velocity using Jira, leading to successful product releases.}
        \resumeItem{Facilitated sprint planning and retrospectives for teams using Jira, ensuring alignment on CI/CD pipelines.}
        \resumeItem{Delivered automated tools using Python, enhancing the team's operational workflows for multiple processes.}
        
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer }{April 2023 -- April 2024}
      {SFU MSA}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{Implemented scalable user authentication for a library inventory management system using React and MongoDB, providing a secure and seamless user experience to over 1500 monthly users.}
        \resumeItem{Attracting 150+ monthly new users by Improved frontend functionality using JavaScript and CSS.}     
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Whale and Dolphin AI Identification} $|$ \emph{Python, Pytorch,  PostgreSQL, Docker}}{June 2024}
          \resumeItemListStart
            \resumeItem{Developed a CNN model for a Kaggle competition using TensorFlow to classify whale and dolphin images,  handling large datasets and achieving an accuracy score of 99\% through extensive hyperparameter tuning.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Developer Coach GPT AI Chatbot} $|$ \emph{React, Typescript, Javascript, AWS, OpenAI API}}{August 2024}
          \resumeItemListStart
            \resumeItem{Implemented robust backend services using React with secure AWS hosting, incorporating monitoring tools to ensure uptime and stability for 1000+ users.}
            \resumeItem{Deployed chatbot infrastructure using Docker and AWS, ensuring scalable and secure hosting.}
            \resumeItem{Achieved \$1000 in revenue by developing the front-end (React, Next.js) and back-end (Node.js, Firebase) of the web app, deploying on AWS S3 to ensure CI/CD.}
          \resumeItemListEnd   
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, Bash, TypeScript, SQL (Postgres)} \\
     \textbf{Infrastructure Tools}{: Docker, Kubernetes, Terraform, Ansible, Prometheus, Grafana} \\
     \textbf{Cloud Platforms}{: AWS (EC2, S3, Lambda), Google Cloud Platform, Azure} \\
     \textbf{DevOps Practices}{: CI/CD pipelines, Infrastructure-as-Code, Monitoring, SaaS Development} \\
     \textbf{Developer Tools}{: Git, Jenkins, PyCharm, IntelliJ, Visual Studio}
    }}
\end{itemize}


% \section{Technical Skills}
%  \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{\item{
%      \textbf{Languages}{: Java, Javascript, Python, C/C++, SQL (Postgres), HTML/CSS, R} \\
%      \textbf{Frameworks}{: React, Node.js, Flask, JUnit, WordPress, Material-UI, FastAPI} \\
%      \textbf{Developer Tools}{: Git, AWS, Docker, Google Cloud Platform, Kubernetes, Visual Studio, PyCharm, IntelliJ, Eclipse} \\
%      \textbf{Libraries}{: pytorch, xgboost, request, stripe, clerk, openai, firebase, pandas, NumPy, Matplotlib}
%     }}
%  \end{itemize}


%-------------------------------------------
\end{document}
